Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-13 paper/galsize_paper.tex
Minor corrections after re-reading draft

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,shibuya_etal15,huang_etal17}.

@@

The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}. Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.

We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}. The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}. In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements. We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius of total $r-$band luminosity, $\rhalf.$

@@

We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM). See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter. To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citep{behroozi_etal10}. For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.  Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}. As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.

Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering, $\wproj(\rproj)$, is in reasonably good agreement with SDSS galaxies. We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$

@@

In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form. Thus this model reproduces the observed $\rhalf-\mstar$ relation by construction. In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$

It is natural to consider the possibility that stellar mass is stripped from satellite galaxies after infall. The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations. In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
\beq
f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
\eeq
For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching. We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data. In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations. As shown in \citet{smith_etal16}, stellar stripping does not begin until $f_{\rm DM}<0.2,$ and the DM halo needs to be stripped to $5\%$ of its initial mass for $50\%$ of stars to be stripped.

@@

As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo. Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01. The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
\beq
\label{eq:fiducial_model}
\rhalf = 0.01\rvir.
\eeq
For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak$ and $\mpeak$ is given by
\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
\eeq
where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}. This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.

@@

In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results. First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  galaxy correlation functions on size remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation. At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly. Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.

@@

Recall that in the $\rvir$-based size model, galaxy size is proportional to halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass. Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.  Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies hosted by halos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history. On the other hand, we define a ``true central" as a galaxy that has never been a satellite. The figure shows that there is a clear trend of sizes decreasing from the central to splashback and to satellite galaxies.

@@

We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the differences of sizes of central and satellites galaxies. The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}. As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies. Thus,  high $\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples. The size dependence of clustering correspondingly weakens and nearly disappears for samples with largest $\mstar$.

Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained by the same principles.  It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}. Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering. For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of halo masses occupied by the satellites. With the impact of satellites reduced, the relative clustering of centrals becomes more important. In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.

@@

The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing. Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.

@@

The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}. For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies. This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.

@@

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}. In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.

@@

Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).

@@

In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and sizes together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge. Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques. For example, it is common to ``deproject" two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately. The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately, and for each model galaxy the projected size can be computed self-consistently with the modeled value of ${\rm B/T}.$ This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites having smaller sizes than centrals is due to differences in ${\rm B/T}.$

@@

Our python code is publicly available on GitHub;\footnote{\url{https://github.com/aphearin/galsize_models}} we intend for this to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web. Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.

@@

We thank the {\tt Astropy} developers for the package-template \citep{astropy}, and {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, IPython, Matplotlib, and GitHub for their extremely useful free software. While writing this paper we made extensive use of the Astrophysics Data Service (ADS) and {\tt arXiv} preprint repository.

@@

Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted. We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe. We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.

>>>>

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.

@@

The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}. Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.

We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}. The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}. In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements. We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the projected half-light radius of total $r-$band luminosity, $\rhalf.$

@@

We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM). See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter. To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}. For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.  Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}. As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.

Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering is in reasonably good agreement with SDSS galaxies. We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$

@@

In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction. In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at the observed $\median{\rhalf}{\mstar}.$

It is natural to consider the possibility that stellar mass is stripped from satellite galaxies after infall. The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations. In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
\beq
f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
\eeq
For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching. We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data. In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations. As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and the DM halo needs to be stripped to $\sim5\%$ of its initial mass for $\sim50\%$ of stars to be stripped.

@@

As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo. Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01. The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
\beq
\label{eq:fiducial_model}
\rhalf = 0.01\rvir
\eeq
For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
\eeq
where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}. This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.

@@

In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results. First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation. At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly. Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.

@@

Recall that in the $\rvir$-based size model, galaxy size is proportional to halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass. Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.  Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies living in subhalos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history. On the other hand, we define a ``true central" as a galaxy that has never been a satellite. The figure shows that there is a clear trend of sizes decreasing from the central to splashback to satellite galaxies.

@@

We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the different of size of centrals and satellites. The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}. As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies. Thus,  high-$\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples. The size dependence of clustering correspondingly weakens and nearly disappears for samples with large $\mstar$.

Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained by the same principles.  It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}. Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering. For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of host halo masses occupied by the satellites. With the impact of satellites reduced, the relative clustering of centrals becomes more important. In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.

@@

The success of the $\rvir$-based model in predicting the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing. Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.

@@

The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}. For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies. This result is in good agreement with the clustering measurements in Figure \ref{fig:colorclustering}, which show the same trend.

@@

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}. In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.

@@

Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios, because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).

@@

In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge. Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques. For example, it is common to de-project two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately. The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more apples-to-apples comparison to observations of projected size. This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$

@@

Our python code has been publicly available on GitHub\footnote{\url{https://github.com/aphearin/galsize_models}} since the inception of the project; we intend for this code to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web. Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.

@@

We thank the {\tt Astropy} developers for the package-template \citep{astropy}, as well as the developers of {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, Jupyter \citep{jupyter}, IPython \citep{ipython}, Matplotlib \citep{matplotlib}, and GitHub for their extremely useful free software. While writing this paper we made extensive use of the Astrophysics Data Service (ADS) and {\tt arXiv} preprint repository.

@@

Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted. We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host model galaxies. We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.
